Kindly Bent to Free Us

### 2019-11-15 kindly/infer/exampleconstr.tex
Improve placement of figures.
Reformat the annex a bit.
Fix all the remaining borked formating.

We now demonstrate the constraint solving
algorithm presented in \cref{infer:solving}.
Let us consider the expression $\lam{f}{\lam{x}{(\app{f}{x},x)}}$.
The application of our inference algorithm yields the following constraints:
%
\begin{align*}
  \E &= (\tvar_f : \kvar_f)
  (\tvar_x : \kvar_x)\dots
  &C &= (\tvar_f \leq \gamma \tarr{\kvar_1} \beta )
  \Cand
  (\gamma \leq \tvar_x)
  \Cand
  (\beta * \tvar_x \leq \alpha_r)
  \Cand
  (\kvar_x \leq \kun)
\end{align*}

@@

and the following kind constraints: 
\begin{gather*}
  \Cproj{\kvar_r}\Cproj{\kvar_f}\Cproj{\kvar_x}
  (\kvar_x \leq \kun)
  \Cand
  (\kvar_\gamma \leq \kvar_x)
  \Cand
  (\kvar_x \leq \kvar_r)
  \Cand
  (\kvar_\beta \leq \kvar_r)
  \Cand
  (\kvar_3 \leq \kvar_f)
  \Cand
  (\kvar_f \leq \kvar_1)
\end{gather*}
Since $\kvar_r$, $\kvar_f$ and $\kvar_x$ are not present in the type skeleton,
they are existentially quantified.

@@

\begin{figure}[!hb]
  \centering
  \begin{minipage}{0.5\linewidth}
  \centering
  \begin{tikzpicture}[every edge/.style=[link,->,>=latex,thick]]
    \node (U) {$\kun$} ;
    \node[above left=of U] (x) {$\kvar_x$} ;
    \node[above=of x] (r) {$\kvar_r$};
    \node[left=of x] (g) {$\kvar_\gamma$} ;
    \node[right=of x] (b) {$\kvar_\beta$} ;
    \node[right=of b] (3) {$\kvar_3$} ;
    \node[above=of 3] (f) {$\kvar_f$} ;
    \node[above=of f] (1) {$\kvar_1$} ;

@@

    \begin{scope}[on background layer]
      \node[fill=green!20,draw=green,
      inner sep=-1mm,ellipse,rotate fit=-20,fit=(U) (x) (g)] {};
      \node[fill=red!20,draw=red, inner sep=-2pt, circle,fit=(r)] {};
      \node[fill=red!20,draw=red, inner sep=-2pt, circle,fit=(f)] {};
    \end{scope}
  \end{tikzpicture}
    \caption{Graph representing the example constraints}
    \label{example:graph}
\end{minipage}~
\begin{minipage}{0.5\linewidth}
  \centering
  \begin{tikzpicture}[every edge/.style=[link,->,>=latex,thick]]
    \node (b) {$\kvar_\beta$} ;
    \node[right=of b] (3) {$\kvar_3$} ;
    \node[above=of 3] (f) {} ;
    \node[above=of f] (1) {$\kvar_1$} ;

@@

  \end{tikzpicture}
    \caption{Final state of the graph}
    \label{example:graph:final}
\end{minipage}
\end{figure}

>>>>

We now demonstrate the constraint solving
algorithm presented in \cref{infer:solving}
on the expression $\lam{f}{\lam{x}{(\app{f}{x},x)}}$.
The application of our inference algorithm yields the following constraints:
%
\begin{align*}
  \E &= (\tvar_f : \kvar_f)
  (\tvar_x : \kvar_x)\dots\\
  C &= (\tvar_f \leq \gamma \tarr{\kvar_1} \beta )
  \Cand
  (\gamma \leq \tvar_x)
  \Cand
  (\beta * \tvar_x \leq \alpha_r)
  \Cand
  (\kvar_x \leq \kun)
\end{align*}

@@

and the following kind constraints: 
\[\begin{aligned}
  \Cproj{\kvar_r}\Cproj{\kvar_f}\Cproj{\kvar_x}{}&
  (\kvar_x \leq \kun)
  \Cand
  (\kvar_\gamma \leq \kvar_x)
  \Cand
  (\kvar_x \leq \kvar_r)
  \Cand\\
  &(\kvar_\beta \leq \kvar_r)
  \Cand
  (\kvar_3 \leq \kvar_f)
  \Cand
  (\kvar_f \leq \kvar_1)
\end{aligned}\]
Since $\kvar_r$, $\kvar_f$ and $\kvar_x$ are not present in the type skeleton,
they are existentially quantified.

@@

\begin{figure}[tbp]
  \centering
  \begin{tikzpicture}[every edge/.style=[link,->,>=latex,thick]]
    \node (U) {$\kun$} ;
    \node[above left=of U] (x) {$\kvar_x$} ;
    \node[above=of x] (r) {$\kvar_r$};
    \node[left=of x] (g) {$\kvar_\gamma$} ;
    \node[right=of x] (b) {$\kvar_\beta$} ;
    \node[right=of b] (3) {$\kvar_3$} ;
    \node[above=of 3] (f) {$\kvar_f$} ;
    \node[above=of f] (1) {$\kvar_1$} ;

@@

    \begin{scope}[on background layer]
      \node[fill=green!20,draw=green,
      inner sep=-1mm,ellipse,rotate fit=-20,fit=(U) (x) (g)] {};
      \node[fill=red!20,draw=red, inner sep=-2pt, circle,fit=(r)] {};
      \node[fill=red!20,draw=red, inner sep=-2pt, circle,fit=(f)] {};
    \end{scope}
  \end{tikzpicture}
    \caption{Graph representing the example constraints}
    \label{example:graph}

  \begin{tikzpicture}[every edge/.style=[link,->,>=latex,thick]]
    \node (b) {$\kvar_\beta$} ;
    \node[right=of b] (3) {$\kvar_3$} ;
    \node[above=of 3] (f) {} ;
    \node[above=of f] (1) {$\kvar_1$} ;

@@

  \end{tikzpicture}
    \caption{Final state of the graph}
    \label{example:graph:final}
\end{figure}

### 2019-11-15 kindly/sdtyping/extra.tex
Fix all the remaining borked formating.

\begin{lemma}[Uniqueness]
  Given $(C_1,\unif_1)$ and $(C_2,\unif_2)$ such that
  $\unif_1 C_1 \equivC \unif_2 C_2$, then
  $\normalize{C_1}{\unif_1}$ and $\normalize{C_2}{\unif_2}$
  are identical up to $\alpha$-renaming.
\end{lemma}
\begin{proof}
  In \cref{lemma:normalform}, we have showed that all the steps of the
  normalization procedure preserve equivalence.
  Since $\unif_1 C_1 \equivC \unif_2 C_2$, equivalence between
  the two results of the normalization procedures is preserved for all steps.

@@

\begin{theorem}
  $\CL$ has the principal constraint property,
  $\operatorname{normalize}$ computes principal normal forms for $\CL$
  and $\CL$ is regular.
\end{theorem}

>>>>

\begin{lemma}[Uniqueness]
  Given $(C_1,\unif_1)$ and $(C_2,\unif_2)$ such that
  $\unif_1 C_1 \equivC \unif_2 C_2$,\\
  then
  $\normalize{C_1}{\unif_1}$ and $\normalize{C_2}{\unif_2}$
  are identical up to $\alpha$-renaming.
\end{lemma}
\begin{proof}
  In \cref{lemma:normalform}, we have showed that all the steps of the
  normalization procedure preserve equivalence.
  Since $\unif_1 C_1 \equivC \unif_2 C_2$, equivalence between
  the two results of the normalization procedures is preserved for all steps.

@@

\begin{theorem}
  $\CL$ has the principal constraint property,\\
  $\operatorname{normalize}$ computes principal normal forms for $\CL$
  and $\CL$ is regular.
\end{theorem}
